---
title: "Plots"
author: "Satya Batna"
date: "2025-10-30"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(plotly)
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(rating = review_scores_location / 2) |>
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) |>
  filter(
    !is.na(rating), 
    neighbourhood_group == "Queens",
    room_type == "Entire home/apt",
    price %in% 100:700)
```

This scatterplot shows the geographic distribution of entire-home Airbnb listings in Queens from 100 to 700 dollaras price range, with point color representing price. Higher-priced listings cluster more heavily around popular areas. 

```{r plot1, echo=FALSE}
nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |> 
  plot_ly(
    x = ~lat, y = ~long, 
    type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

This bar plot displays the number of listings across neighborhoods in Queens. The highest listings are in Long City Island, Sunnyside and Jackson Heights (my personal fav place).

```{r plot2, echo=FALSE}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(
    x = ~neighbourhood, y = ~n, 
    color = ~neighbourhood, 
    type = "bar")
```

This interactive scatterplot visualizes price variation across Queens based on listing location. Dense point clusters and color gradients help reveal areas with both high listing volume and higher rental prices.
```{r plot3, echo=FALSE}
scatter_ggplot = 
  nyc_airbnb |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.25) +
  coord_cartesian()

ggplotly(scatter_ggplot)
